---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, eval = TRUE, comment = "#>")
```

**Collaborative project for Lab 5 in Advanced R Programming course (Stastistics &amp; Machine Learning MSc - LiU)**

This is the Lab 6 report regarding the Knapsack problem. We have implemented three different approaches for this problem: the brute force search, dynamic and greedy heuristic methods. The vignette includes the examples and results of these approaches, as well as answering questions about time and performance of the algorithms.

**Group 16:**

* Vasileios Karapoulios - vaska579

* Stylianos Sidiropoulos - stysi607


```{r initial_setup}
# Import libraries
library(Lab6)
library(parallel)

#Set knapsack dataset
set.seed(42)
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
```

## Brute Force Search

Below there are some examples for the Brute Force approach to the Knapsack problem:

```{r brute_example_1}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r brute_example 2}
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```

**Question: ** How much time does it take to run the algorithm for `n = 16` objects?

**Answer: ** 

For `W = 2000`:

```{r brute_answer}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000))
```

## Dynamic programming

Below there are some examples for the Dynamic approach to the Knapsack problem:

```{r dynamic_example_1}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```

```{r dynamic_example_2}
knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```

**Question: ** How much time does it take to run the algorithm for `n = 500` objects?

**Answer: ** 

For `W = 2000`:

```{r dynamic_answer}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 2000))
```

## Greedy heuristic

Below there are some examples for the Dynamic approach to the Knapsack problem:

```{r greedy_example_1}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
```{r greedy_example_2}
greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

**Question: ** How much time does it take to run the algorithm for `n = 1000000` objects?

**Answer: ** 

For `W = 2000`:

```{r greedy_answer}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 2000))
```

## Profile and Optimize code

**Question: ** What performance gain could you get by trying to improving your code?

**Answer: ** Profiling and optimizing the code, we can identify and fix bottlenecks.  We can identify the causes that make the code slow and consuming system resources. The main performance gain we get by optimizing the code is that it takes less time to excecute the program and produce results with the least usage of system resources.

##  Parallelize brute force search

Brute Force Knapsack with Parallelization:

```{r eval=FALSE}
system.time(brute_force_knapsack(x = knapsack_objects[1:10,], W = 3500, parallel = TRUE))
```

Brute Force Knapsack without Parallization:

```{r eval=FALSE}
system.time(brute_force_knapsack(x = knapsack_objects[1:10,], W = 3500, parallel = FALSE))
```

**Question: ** What performance gain could you get by parallelizing brute force search?

**Answer: ** Parallelization is one of the solutions for the code to run faster. The performance gain we get by parallelizing the code is again the improvement of the execution time of the code. This performance gain is achieved by running the program in multiple processors of our system simultaneously.